---
title: "Tutorial: Introduction to High Throughput DNA Sequence Data
    Analysis Using R / Bioconductor"
author: Martin Morgan <martin.morgan@roswellpark.org>
date: "Tuesday, 8 March, 2016"
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  % \VignetteIndexEntry{Tutorial: Introduction to High Throughput DNA Sequence Data Analysis Using R / Bioconductor}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
options(width=100)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```


# Introduction

## _R_

## _Bioconductor_

## Sequence Analysis

# Case Study: RNA-Seq Differential Expression

## Preparation

## Analysis Pipeline

## Statistical Considerations

## Downstream Annotation

# Challenges & Solutions

## Reproducibility

## Interoperability

## Scalability

# From Script to Package

# Acknowledgments

Funding

- NCI / NHGRI
- NCI / ITCR
- EC / SOUND

Personnel

- Current and recent team members
- Technical Advisory Board
- Scientific Advisory Board

```{r sessionInfo}
sessionInfo()
```
