---
title: "Tutorial: Introduction to High Throughput DNA Sequence Data
    Analysis Using R / Bioconductor"
author: Martin Morgan <martin.morgan@roswellpark.org>
date: "Tuesday, 8 March, 2016"
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  % \VignetteIndexEntry{Tutorial: Introduction to High Throughput DNA Sequence Data Analysis Using R / Bioconductor}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
options(width=100)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
    library(ggplot2)
})
```

# Introduction

## _R_

- [r-project.org][]: "A free software environment for statistical
  computing and graphics"

Data & functions

Vectors

- logical (`c(TRUE, FALSE)`), integer (`1:5`), numeric (`rnorm(10)`),
  character (`c("alpha", "beat")`), complex

- statistical concepts: missing values (`NA`), factors
  (`factor(c("Female", "Male"))`), formulas (`y ~ x`)

- vectorized

```{r vectors}
x <- rnorm(1000)
y <- x + rnorm(1000)
plot(y ~ x)
```

Objects: classes and methods

- coordinated manipulation of related data

- simple _classes_, e.g., `data.frame()`, `matrix()`

- more complicated classes, e.g., `lm()`

- manipulation via _methods_

```{r classes}
df <- data.frame(Y = y, X = x)
fit <- lm(Y ~ X, df)
plot(Y ~ X, df)
abline(fit, col="red", lwd=2)
anova(fit)
```

Packages

- base & recommended
    - e.g., `stats`, `graphics`, `Matrix`

- contributed
    - e.g., `ggplot2`, `dplyr`, `ade`
    - discovery: [CRAN][] landing pages and task views
    - installation: `install.packages()` (or `biocLite()`, below)

```{r ggplot2, warning=FALSE}
library(ggplot2)
ggplot(df, aes(x=X, y=Y)) + geom_point() + geom_smooth(color="blue") +
    geom_smooth(method="lm", color="red")
```

Help!

- `help.start()`
- `?rnorm`
- `?"plot<tab>...`

## _Bioconductor_

- [bioconductor.org][]: "Analysis and comprehension of high-throughput
  genomic data"

Biological domains

Principles

Installation and use

- discovery: [biocViews][], package landing pages (e.g., [DESeq2][])
- installation: `biocLite("DESeq2")`; also works for CRAN & github
  packages
- help! -- [support.bioconductor.org][]

## Sequence Analysis

# Case Study: RNA-Seq Differential Expression

## Preparation

## Analysis Pipeline

## Statistical Considerations

## Downstream Annotation

# Challenges & Solutions

## Reproducibility

## Interoperability

## Scalability

# From Script to Package

# Acknowledgments

Funding

- NCI / NHGRI
- NCI / ITCR
- EC / SOUND



- Current and recent team members
- Technical Advisory Board
- Scientific Advisory Board

```{r sessionInfo}
sessionInfo()
```

[r-project.org]: https://r-project.org
[CRAN]: https://cran.r-project.org
[bioconductor.org]: https://bioconductor.org
[support.bioconductor.org]: https://support.bioconductor.org
